---
title: "Test Report Render"
author: "David Hughes"
date: "`r Sys.Date()`"
papersize: a4
fontsize: 12pt
mainfont: Arial
output: 
  pdf_document:
    latex_engine: pdflatex
    toc: true
    fig_caption: true
    keep_md: true
    number_sections: true
params: 
 Rdatafile: NA
 out_dir: out_dir
---

\newpage
## what is this?

This report is just an toy example to see if I can create a package that has (1) an embedded png image, (2) a embedded data set to use internal, (3) can generate an Rdata object generated outside the report, but accessed by it to generate figures and tables. 

## load packages

```{r setup, include=TRUE}
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(tidyverse))

knitr::opts_chunk$set(warning=FALSE, echo=TRUE, message=FALSE, 
               results='asis', fig.width=6, fig.height=6 )
```

## load Rdata file for report to us

```{r}
load(params$Rdatafile)
```

\newpage
## A picture of daisy built into package

```{r , out.width = "200px"}
f = system.file("rmarkdown", package="exrender")
pic = file.path( f, "skeleton/daisy.png")
knitr::include_graphics(pic)
```


## print a cars data summary

```{r cars}
knitr::kable(summary(cars))
```

## pressure plot

A random plot of some 

```{r pressure, echo=TRUE, fig.width = 4, fig.height = 3.5}
plot(pressure)
```


\newpage
## plot the ggplot object

We made this image in the make_some_data() function and passed it to the report as a paramater that needed to be loaded.

```{r, fig.width = 8, fig.height = 6}
my_plot
```

\newpage
## make a table 

A table of the first few rows of the embedded data set 'ng_anno'

```{r}
knitr::kable(ng_anno[1:4,])
```



